%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Teaching Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Teaching Assistant | Instructor: Farsad Zamani Boroujeni | \href{https://scholar.google.com/citations?user=RENIRWwAAAAJ&hl=en}{(Scholar)}} % Job title
{Advanced Topics 01 - Deep Learning \& Neural Networks} % Organization
{SRBIAU, Tehran, Iran} % Location
{Jan. 2023 - Jun. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Hands on experience with Tensorflow/Keras}
\item {Design and Implementation of Neural Networks}
\item {Theory and basics of linear algebra and mathematics in Neural Networks}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Teaching Assistant | Instructor: Mahdi Bagherizadeh | \href{https://scholar.google.com/citations?user=mvHPeQwAAAAJ&hl=en}{(Scholar)}} % Job title
{Digital Systems Design} % Organization
{SRBIAU, Tehran, Iran} % Location
{Jan. 2023 - Jun. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designing various logical circuits with different factors}
\item {Theory and basics of FPGA, VLSI, PLD/CPLD}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Teaching Assistant | Instructor: Hamidreza Bolhasani | \href{https://scholar.google.co.in/citations?user=JnHYS6EAAAAJ&hl=en}{(Scholar)}} % Job title
{Python/Tensorflow Workshop} % Organization
{SRBIAU, Tehran, Iran} % Location
{Sept. 2022 - Dec. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Theories of Machine Learning/Deep Learning}
\item {Making Machine Learning models with SKLearn/Tensorflow}
\item {Making Neural Networks and Deep Learning models with Tensorflow} 
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Teaching Assistant | Instructor: Somayeh Khoroush} % Job title
{Microprocessors Lab} % Organization
{SRBIAU, Tehran, Iran} % Location
{Jul. 2022 - Aug. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Simulating AVR microcontrollers with Proteus}
\item {Programming various samples with AVR microcontrollers and C language}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Teacher / Teaching Assitant} % Job title
{Robotics, Programming \& Electronics} % Organization
{Kavosh Creativity House, Tehran, Iran} % Location
{May 2019 - Dec. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Programming for AVR Microchips with C Programming Language}
\item {Running Simulations on AVR Microchips with Proteus PCB Design and Circuit Simulator}
\item {Basics of Electronics \& Soldering}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
